\chapter{General remarks}
\label{ch:general_remarks}

%------------------------------------

\section{Notes on the assignment}
\label{sec:notes_on_ass}

None of the assignments for the Software Architectures course were submitted in the first examination period due to personal reasons.
Because of this, all of the code written for this assignment is written specifically for the second examination period.
All code was written by using the course material and the online Akka Play documentation\footnote{\url{https://www.playframework.com/documentation/2.8.x/Home}}.
The solution of exercise 7 was used as a starter template for this project.
A previous MEAN stack school project of mine based on Bootstrap, CarMeets \citep{github_carmeets}, was used as concept and styling (HTML + CSS) inspiration for this project.

%------------------------------------

\section{Important files}
\label{sec:important_files}

All code written is available on the GitHub repository for this assignment \citep{github_project}. 
Rights to this private GitHub repository can be granted upon request. 
A copy of this GitHub repository is accompanied by this report.
An overview of important files is given below:
\begin{itemize}
    \item \texttt{README.md}
    \begin{itemize}
        \item General information of the GitHub repository as well as some technical details about the used environment and how to run the project. The general flow of the application for the end-user is also demonstrated with some screenshots. The pre-loaded account information is also supplied here.
    \end{itemize}
    \item \texttt{assignment.pdf}, \texttt{Lennert-Bontinck-SA2.pdf} and \texttt{report/}
    \begin{itemize}
        \item The assignment PDF, this report and the source files of the report. A VUB themed \LaTeX{} template by \citet{latex_template} was used to create this report.
    \end{itemize}
    \item \texttt{code/Lennert-Bontinck-SA2/}
    \begin{itemize}
        \item The folder containing the code of the assignment solution.
        \item Instructions on how to run the code are available in the \texttt{README.md} file.
    \end{itemize}
\end{itemize}